Data Preparation, Integration and Cleaning

### 2017-03-09 abbDataPrep_Script.Rmd
Updates to maps

  # Set colors
  g.cols <- abb.col[c(2, 10, 9)]

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=g.cols, labels=c('Inner      ',
                                              'Middle      ',
                                              'Outer')) +
    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    ggtitle("Melbourne Suburb Classifications")+
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
    geom_point(data=str.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('AirBNB Location\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long Term Rental Location\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('Long Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

>>>>

  # Set colors
  g.cols <- c('grey10', 'grey40', 'grey70')

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=g.cols, labels=c('Inner      ',
                                              'Middle      ',
                                              'Outer')) +
    geom_path(data=subs[subs$des=='Outer', ], 
              aes(x=long, y=lat, group=group), col='white', size=.1,
              linetype=1) +

    geom_path(data=subs[subs$des=='Middle', ], 
              aes(x=long, y=lat, group=group), col='grey70', size=.1,
              linetype=1) +

    geom_path(data=subs[subs$des=='Inner', ], 
              aes(x=long, y=lat, group=group), col='grey40', size=.1,
              linetype=1) +

    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    #ggtitle("Melbourne Suburb Classifications")+
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Long Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))
